Call Center Regression Data Analysis

### 2022-11-11 Manuscript/Manuscript.tex
commit #Introduction

  \citep{evensen1999effective} goes into detail about effectve service delivery stating the expecations of customers are of "function of
the customer's own experiences...and when judging their own service quality, financial instiutions need to evalute themselves on 
objective measures which span across industries". When taking this into consideration, I focused my models on using calls per agent approach,
so agents are not overworked and can treat each member with respect and honor to represent the business in good light. \citep{avramidis2005modeling} confirms
this as it is described as the "call-to-agent" problem, and that an efficiency-driven call center is important.

  The contributions of the paper

@@

\section*{Results}
\citep{avramidis2005modeling}
\citep{evensen1999effective}
\citep{ibrahim2016modeling}

>>>>

  \citep{evensen1999effective} goes into detail about effectve service delivery stating the expecations of customers are of "function of
the customer's own experiences...and when judging their own service quality, financial instiutions need to evalute themselves on 
objective measures which span across industries".When taking this into consideration, I focused my models on using a calls per agent approach,
so agents are not overworked and can treat each member with respect and honor to represent the business in good light. \citep{avramidis2005modeling} confirms
this as it is described as the "call-to-agent" problem, and that an efficiency-driven call center is important.

  The contributions of the paper creates models on the basis to maximize quality of the service in relation to the number of agents. 
Based on this, models were created to minimize:
1)WaitTime
2)CallTime
3)Reduce GoalTime not being Met
4)Reduce Calls not being Handled
The rest of the paper will go through the dataset and breaking it up to present a clear view on the historical data. I have also created a 
forecast on the projected call volume throughout a week through a 15 minute interval.

@@
